---
title: "CheWei Meng Final"
author: "CheWei Meng"
date: "2022-08-05"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Background:Data

**Exploratory data analysis of wine reviews given by different customer and tasters across different countries.**

**Source:**
Kaggle data,web crawling reviews

[linked phrase] https://www.kaggle.com/code/sudhirnl7/wine-recommender/notebook

**Analysis Questions/Potential Insights**

-Country wise wine volume

-Average rating of wine by country 

-Price and Point Correlation:Is there a correlation between price and points?

-What are the top-ten most popular grape varieties among the tasters ? 

-What kind of flavor profile do consumers prefer?


## Method:Data Cleaning
Brief of Data
```
library(dplyr)
library(tidytext)
library(ggplot2)
str(dataset1)
summary(dataset1)
```
```{r}
 <-
library(tidytext)
library(ggplot2)
dataset1 <- read.csv("winer.csv")
```
Examine Data Type
```
str(dataset1)
```
```{r}
str(dataset1)

```
```
summary(dataset1)
```

```{r}
summary(dataset1)
```

Drop unnecessary columns
```{r} 
datatest <- subset(dataset1, select = -taster_name)
datatest <- subset(datatest,select=-region_2)
datatest <- subset(datatest,select=-X)
datatest <- subset(datatest,select=-designation)
```
```
datatest <- subset(dataset1, select = -taster_name)
datatest <- subset(datatest,select=-region_2)
datatest <- subset(datatest,select=-X)
datatest <- subset(datatest,select=-designation)
```

Discover NA and missing data
```{r} 
sum(is.na(datatest))
datatest <- na.omit(datatest)
```
```
sum(is.na(datatest))
datawine <- na.omit(datatest)
```


Dataset trimmed down 8996 NA value


Convert blank rows to NA 
```{r} 
datatest$region_1[datatest$region_1==""| datatest$region_1==" " ]<-NA
datatest$country[datatest$country==""| datatest$region_1==" " ]<-NA
datatest$description[datatest$description==""| datatest$description==" " ]<-NA
datatest$points[datatest$points==""| datatest$points==" " ]<-NA
datatest$price[datatest$price==""| datatest$price==" " ]<-NA
datatest$taster_twitter_handle [datatest$taster_twitter_handle ==""| datatest$taster_twitter_handle ==" " ]<-NA
datatest$title [datatest$title ==""| datatest$title ==" " ]<-NA

```
```
datatest$region_1[datatest$region_1==""| datatest$region_1==" " ]<-NA
datatest$country[datatest$country==""| datatest$region_1==" " ]<-NA
datatest$description[datatest$description==""| datatest$description==" " ]<-NA
datatest$points[datatest$points==""| datatest$points==" " ]<-NA
datatest$price[datatest$price==""| datatest$price==" " ]<-NA
datatest$taster_twitter_handle [datatest$taster_twitter_handle ==""| datatest$taster_twitter_handle ==" " ]<-NA
datatest$title [datatest$title ==""| datatest$title ==" " ]<-NA
```
Check total NA value 

```{r} 
colSums(is.na(datatest))
sum(is.na(datatest))
```
```
colSums(is.na(datatest))
sum(is.na(datatest))
```
Create new cleaned dataframe
```
datatest_clean <- na.omit(datatest)
```
```{r} 
datatest_clean <- na.omit(datatest)
```

Dataset trimmed down 46683

Rename long variable name

```
datatest_clean <- plyr::rename(datatest_clean, c("region_1" = "subregion","taster_twitter_handle"="taster"))
```

```{r} 
datatest_clean <- plyr::rename(datatest_clean, c("region_1" = "subregion","taster_twitter_handle"="taster"))
```

## Analysis
**Price Point relation**
Create price/points matrix
There is a rather positive relationship between price and point,in the wine industry sometimes you can find hidden gems with cheaper price yet high ranking points.


```
price_points <- data.frame(datatest_clean$points,datatest_clean$price)
cor(price_points )
```
```{r}
price_points <- data.frame(datatest_clean$points,datatest_clean$price)
cor(price_points )
```

**Visualization**

Price Point Scatter Plot
```
price_points_plot <-ggplot(price_points,aes(x=datatest_clean$points,y=datatest_clean$price))+geom_point(na.rm = TRUE)+geom_smooth(method="glm")
price_points_plot
```
```{r}
price_points_plot <-ggplot(price_points,aes(x=datatest_clean$points,y=datatest_clean$price))+geom_point(na.rm = TRUE)+geom_smooth(method="glm")
price_points_plot
```
```
lm(datatest_clean$price~datatest_clean$points,data =price_points)
```
```{r}
lm(datatest_clean$price~datatest_clean$points,data =price_points)
```

**WinePrice = 6.112  * WinePoints-504.938**


**Example:**
Wine could be consider as a bargain if the wine has rating of 95 or above yet cost less than 75$.


**Volume of wine by country**

Create new price range
wines that are above 1000 and below 15 dollars
```
new_datatest_clean<-filter(datatest_clean,datatest_clean$price<=1000 & datatest_clean$price>=15)
```
```{r}
new_datatest_clean<-filter(datatest_clean,datatest_clean$price<=1000 & datatest_clean$price>=15)
```

Convert country variable into factor variable
```
new_datatest_clean$country <- factor(new_datatest_clean$country,levels = c("US", "France", "Italy", "Spain","Argentina","Australia","Canada"))

```

```{r}
new_datatest_clean$country <- factor(new_datatest_clean$country,levels = c("US", "France", "Italy", "Spain","Argentina","Australia","Canada"))
```
**Visualization:Bar Chart**
```
ggplot(new_datatest_clean,aes(x= country,y=price))+geom_bar(aes(fill=country),stat ="identity")
```
```{r}
ggplot(new_datatest_clean,aes(x= country,y=price))+geom_bar(aes(fill=country),stat ="identity")
```

**Most popular grape variety**
New dataframe with point,price and variety
Sort the most appeared varieties on a decreasing order
```
popular_grapes<- datatest_clean[,c(3,4,9)]
popular_grapes_n<- popular_grapes %>% count(variety, sort = TRUE)
```
```{r}
popular_grapes<- datatest_clean[,c(3,4,9)]
popular_grapes_n<- popular_grapes %>% count(variety, sort = TRUE)
head(popular_grapes_n,10)
```
Drop non meaningful rows:Red Blend &Rose
```
popular_grapes_n<- popular_grapes_n[-c(3,7),]
```
```{r}
popular_grapes_n<- popular_grapes_n[-c(3,7),]
```

**Top 10 popular grape variety:**
Red Wine:Pinot Noir/Cabernet Sauvignon/Bordeaux-style Red Blend/Syrah/Malbec/Sangiovese/Nebbiolo
White Wine:Chardonnay/Sauvignon Blanc/Riesling

**Average Wine Points by country**
Find mean points for each country
```
country_point <- datatest_clean[,c(1,3)]
avg_country_price <- filter(filter(country_point,country %in% c("US")))
us_points <- mean(avg_country_price$points)

avg_country_price <- filter(filter(country_point,country %in% c("France")))
france_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Italy")))
Italy_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Spain")))
Spain_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Australia")))
Australia_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Argentina")))
Argentina_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Canada")))
Canada_points <- mean(mean(avg_country_price$points))
```
```{r}
country_point <- datatest_clean[,c(1,3)]
avg_country_price <- filter(filter(country_point,country %in% c("US")))
us_points <- mean(avg_country_price$points)

avg_country_price <- filter(filter(country_point,country %in% c("France")))
france_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Italy")))
Italy_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Spain")))
Spain_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Australia")))
Australia_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Argentina")))
Argentina_points <- mean(mean(avg_country_price$points))

avg_country_price <- filter(filter(country_point,country %in% c("Canada")))
Canada_points <- mean(mean(avg_country_price$points))
```

Creat  Barchart
```
country <- c("US","France","Italy","Spain","Australia","Argentina","Canada")
country_point_1 <- c(us_points,france_points,Italy_points,Spain_points,Australia_points,Argentina_points,Canada_points)

country_point_f <- data.frame(country_point_1,country)

country_point_f$country <- factor(country_point_f$country,levels = c("Canada", "US", "Italy", "Australia","France","Spain","Argentina"))

ggplot(country_point_f,aes(x= country,y=country_point_1))+geom_bar(aes(fill=country),stat ="identity")
```
```{r}
country <- c("US","France","Italy","Spain","Australia","Argentina","Canada")
country_point_1 <- c(us_points,france_points,Italy_points,Spain_points,Australia_points,Argentina_points,Canada_points)

country_point_f <- data.frame(country_point_1,country)

country_point_f$country <- factor(country_point_f$country,levels = c("Canada", "US", "Italy", "Australia","France","Spain","Argentina"))

ggplot(country_point_f,aes(x= country,y=country_point_1))+geom_bar(aes(fill=country),stat ="identity")
```
## Reviews Text Analysis

Tokenization,Omit stop words(the/an/that) from tidytext package
```
wine_review <- 
  datatest_clean %>% unnest_tokens(output=word,input=description) %>% 
  anti_join(stop_words,by="word") %>% 
  distinct() %>% 
  count(word,sort=TRUE)
```
```{r}
wine_review <- 
  datatest_clean %>% unnest_tokens(output=word,input=description) %>% 
  anti_join(stop_words,by="word") %>% 
  distinct() %>% 
  count(word,sort=TRUE)
```
Create different wine aroma discriptors for filter
```
fruity<-c("berry", "grape", "cherry", "strawberry", "boysenberry", "cassis", "blueberry", "blackberry","black cherry","citrus" ," apple", "pear", "pineapple")
tertiary<-c("tobacco", "truffle", "earth", "spice box", "chocolate", "smoke", "crushed stone","cigar box")
oak<-c("coffee", "vanilla","chocolate")
```
```{r}
fruity<-c("berry", "grape", "cherry", "strawberry", "boysenberry", "cassis", "blueberry", "blackberry","black cherry","citrus" ," apple", "pear", "pineapple")
tertiary<-c("tobacco", "truffle", "earth", "spice box", "chocolate", "smoke", "crushed stone","cigar box")
oak<-c("coffee", "vanilla","chocolate")
```

Filter

```
aroma1<-ifelse(wine_review$word %in% fruity,"fruit",(ifelse(wine_review$word %in% oak,"oak",(ifelse(wine_review$word %in% tertiary,"tertiary","non")))))
wine_review$aroma <- aroma1
wine_review1<-filter(wine_review,aroma %in% c("fruit","oak","tertiary"))
wine_review1$aroma <- factor(wine_review1$aroma,levels = c("fruit","oak","tertiary"))
```
```{r}
aroma1<-ifelse(wine_review$word %in% fruity,"fruit",(ifelse(wine_review$word %in% oak,"oak",(ifelse(wine_review$word %in% tertiary,"tertiary","non")))))
wine_review$aroma <- aroma1
wine_review1<-filter(wine_review,aroma %in% c("fruit","oak","tertiary"))
wine_review1$aroma <- factor(wine_review1$aroma,levels = c("fruit","oak","tertiary"))

```




Visualization
```
ggplot(wine_review1,aes(x= word,y=n))+geom_bar(aes(fill=aroma),stat ="identity")
```
```{r}
ggplot(wine_review1,aes(x= word,y=n))+geom_bar(aes(fill=aroma),stat ="identity")
```



## Conclusion
1.Top-ten popular grape varieties are:
Red Wine:Pinot Noir/Cabernet Sauvignon/Bordeaux-style Red Blend/Syrah/Malbec/Sangiovese/Nebbiolo 
White Wine:Chardonnay/Sauvignon Blanc/Riesling

2.There is a positive relationship between price and points,you pay what you drink.But it is possible to find hidden gems.
WinePrice = 6.112 * WinePoints-504.938
Keep a tab on this formula and bring them with you at a wine storeï¼

3.Us has the most volume of wine in terms of 15~1000 price range.

4.In the realm of the this data set the quality of wine have no significant difference.

5.Consumers prefer more fruit characters in wines 

